Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-29 paper/gd1.tex
Fill in XXs

We retrieve \gaia\ data along the previously-identified track of the GD-1 stream
from the \gaia\ science archive\footnote{\url{https://gea.esac.esa.int/}} by
selecting all sources with small parallax, $\varpi < 1~\textrm{mas}$, and use a
set of spherical polygons to select batches of stars that have small latitude in
the heliocentric GD-1 coordinate system, $(\phi_1, \phi_2)$, defined in
\cite{Koposov:2010}.\footnote{This transformation is implemented using the
\package{Astropy} (\citealt{astropy}) coordinate transformation framework in the
\package{Gala} \texttt{Python} package (\citealt{gala}).}
We convert the sky coordinates and proper motions of the parallax-selected stars
to the GD-1 stream coordinate system, and correct the proper motions for solar
reflex motion by assuming that stars at a given stream longitude, $\phi_1$, have
a distance given by the linear relationship $d(\phi_1) = (0.05 \, \phi_1 +
10)~\textrm{kpc}$.
For the solar velocity in a Galactocentric rest frame, we use $\bs{v}_\odot =
(11.1, 232.24, 7.25)~\kms$ (\citealt{Schonrich:2010, Bovy:2015}).
\figurename~\ref{fig:selection} (top right) shows the distribution of stars with
$|\phi_2| < XX^\circ$ in solar-reflex-corrected proper motion components in the
GD-1 coordinate system, $\mu_{\phi_1, \odot}$ (which includes the $\cos{\phi_2}$
term) and $\mu_{\phi_2, \odot}$.
GD-1 member stars are visible as the over-density around
$(\mu_{\phi_1, \odot}, \mu_{\phi_2, \odot}) \approx (-8, 0)~\masyr$.

As a first selection of GD-1 candidate member stars, we select stars with proper
motions $XX < \mu_{\phi_1, \odot} < XX~\masyr$ and $XX < \mu_{\phi_2, \odot} <
XX~\masyr$, as visualized by the rectangle in the top right panel of
\figurename~\ref{fig:selection}.
\figurename~\ref{fig:selection} (top left) shows all stars the pass the
selection on proper motion, plotted in the GD-1 coordinate system.
From kinematic selection alone, the stream is identifiable as the over-density
of stars around $\phi_2 = 0$ between longitudes $XX^\circ \lesssim \phi_1
\lesssim XX^\circ$.

@@

To improve the contrast of the stream over the background, we cross-match the
sample to the \pans\ photometric catalog and use the photometry to further clean
the sample.
\figurename~\ref{fig:selection} (bottom right) shows the distribution of
proper-motion-selected candidate stream stars in a de-reddened \pans\
color-magnitude diagram (CMD).
\todo{AB: Did you also cut on $phi_2$?}.
The over-plotted isochrone (red line) is from the MESA Isochrones \& Stellar
Tracks (MIST; \citealt{Dotter:2016, Choi:2016, Paxton:2011}) and represents a
$12~\textrm{Gyr}$ old population with $\feh = -1.XX$ at a distance of $XX~\kpc$.
We use this isochrone to motivate a polygonal selection in de-reddened $g-i$
color and apparent $g$-band magnitude, as visualized by the shaded region in the
bottom right panel of \figurename~\ref{fig:selection}.

>>>>

We retrieve \gaia\ data along the previously-identified track of the GD-1 stream
from the \gaia\ science archive\footnote{\url{https://gea.esac.esa.int/}} by
selecting all sources with small parallax, $\varpi < 1~\textrm{mas}$, and use a
set of spherical polygons to select batches of stars that have small latitude in
the heliocentric GD-1 coordinate system, $(\phi_1, \phi_2)$, defined in
\cite{Koposov:2010}.\footnote{This transformation is implemented using the
\package{Astropy} (\citealt{astropy}) coordinate transformation framework in the
\package{Gala} \texttt{Python} package (\citealt{gala}).}
We convert the sky coordinates and proper motions of the parallax-selected stars
to the GD-1 stream coordinate system, and correct the proper motions for solar
reflex motion by assuming that stars at a given stream longitude, $\phi_1$, have
a distance given by the linear relationship $d(\phi_1) = (0.05 \, \phi_1 +
10)~\textrm{kpc}$.
For the solar velocity in a Galactocentric rest frame, we use $\bs{v}_\odot =
(11.1, 232.24, 7.25)~\kms$ (\citealt{Schonrich:2010, Bovy:2015}).
\figurename~\ref{fig:selection} (top right) shows the distribution of stars with
$|\phi_2| < 1^\circ$ in solar-reflex-corrected proper motion components in the
GD-1 coordinate system, $\mu_{\phi_1, \odot}$ (which includes the $\cos{\phi_2}$
term) and $\mu_{\phi_2, \odot}$.
GD-1 member stars are visible as the over-density around
$(\mu_{\phi_1, \odot}, \mu_{\phi_2, \odot}) \approx (-8, 0)~\masyr$.

As a first selection of GD-1 candidate member stars, we select stars with proper
motions $-9 < \mu_{\phi_1, \odot} < -4.5~\masyr$ and $-1.7 < \mu_{\phi_2, \odot}
< 1~\masyr$, as visualized by the rectangle in the top right panel of
\figurename~\ref{fig:selection}.
\figurename~\ref{fig:selection} (top left) shows all stars the pass the
selection on proper motion, plotted in the GD-1 coordinate system.
From kinematic selection alone, the stream is identifiable as the over-density
of stars around $\phi_2 = 0$ between longitudes $XX^\circ \lesssim \phi_1
\lesssim XX^\circ$.

@@

To improve the contrast of the stream over the background, we cross-match the
sample to the \pans\ photometric catalog and use the photometry to further clean
the sample.
\figurename~\ref{fig:selection} (bottom right) shows the distribution of
proper-motion-selected candidate stream stars in a de-reddened \pans\
color-magnitude diagram (CMD).
\todo{AB: Did you also cut on $phi_2$?}.
The over-plotted isochrone (red line) is from the MESA Isochrones \& Stellar
Tracks (MIST; \citealt{Dotter:2016, Choi:2016, Paxton:2011}) and represents a
$12~\textrm{Gyr}$ old population with $\feh = -1.35$ at a distance of
$7.8~\kpc$.
We use this isochrone to motivate a polygonal selection in de-reddened $g-i$
color and apparent $g$-band magnitude, as visualized by the shaded region in the
bottom right panel of \figurename~\ref{fig:selection}.
